ASYMPTOTIC VALIDITY OF THE BAYES-INSPIRED INDIFFERENCE ZONE PROCEDURE:

### 2015-07-02 paper/wish/wsc15paper.tex
edits to paper to address reviewer 2

Our second example, illustrated in Figure~\ref{fig: tahi2}, is an unknown variance slippage configuration where the variance of the best alternative is 100 times larger than the variance of the other alternatives. Although Theorem~\ref{t:main} applies only to the known-variance version of BIZ, we conjecture that the unknown-variance version of BIZ should exhibit similar behavior.
In this example, we consider $100$ systems with independent normally distributed samples, where $\mu_{100}=\delta,\mu_{99}=0,\dots,\mu_{1}=0$, $\delta$ is within the interval $[0.1,10]$, and $\lambda_{100}=10,\lambda_{99}=\cdots=\lambda_{1}=1$. We set $n_{0}=15$.
As $\delta$ goes to $0$, we observe that the PCS converges to $P^*$, as it did in the known-variance slippage configuration example.
In this example, we have intentionally chosen $n_0$ to be smaller than the recommended value of 100, and have chosen a large variance for the best system, to cause BIZ to fail to meet the IZ guarantee for $\delta>0$.
Increasing the parameter $n_0$ typically causes BIZ to meet the IZ guarantee for all $\delta$, and we recommend a larger value of $n_0$ in practice.

@@

We have proved the asymptotic validity of the Bayes-inspired Indifference Zone
procedure \cite{Frazier:BIZ} when the variances are known.
This algorithm takes fewer samples than other IZ procedures, especially for
problems with large numbers of alternatives, and so characterizing when it
satisfies the indifference-zone guarantee is important for understanding when
it should be used in practice.

>>>>

Our second example, illustrated in Figure~\ref{fig: tahi2}, is an unknown variance slippage configuration where the variance of the best alternative is 100 times larger than the variance of the other alternatives. Although Theorem~\ref{t:main} applies only to the known-variance version of BIZ, we conjecture that the unknown-variance version of BIZ should exhibit similar behavior.
In this example, we consider $100$ systems with independent normally distributed samples, where $\mu_{100}=\delta,\mu_{99}=0,\dots,\mu_{1}=0$, $\delta$ is within the interval $[0.1,10]$, and $\lambda_{100}=10,\lambda_{99}=\cdots=\lambda_{1}=1$. We set $n_{0}=15$.
As $\delta$ goes to $0$, we observe that the PCS converges to $P^*$, as it did in the known-variance slippage configuration example.
In this example, we have intentionally chosen $n_0$ to be smaller than the recommended value of 100, and have chosen a large variance for the best system, to cause BIZ to fail to meet the IZ guarantee for $\delta>0$.
Increasing the parameter $n_0$ typically causes BIZ to meet the IZ guarantee for all $\delta$, and we recommend a larger value of $n_0$ in practice.  The choice of $n_0$, and its impact on PCS, merits further study.

@@

We have proved the asymptotic validity of the Bayes-inspired Indifference Zone
procedure \cite{Frazier:BIZ} when the variances are known.
This algorithm has been observed empirically to take fewer samples than other IZ procedures, especially for
problems with large numbers of alternatives, and so characterizing when it
satisfies the indifference-zone guarantee is important for understanding when
it should be used in practice.
